\chapter*{Acknowledgments}
While many consider writing a PhD thesis to be a mostly personal endeavor, there are always various sources of discourse, collaboration, support and inspiration. 

I would like to express my gratitude towards Prof. Dieter W. Fellner for the guidance and support I have received over the last years. Likewise, I want to thank Prof. xxx for agreeing to evaluate this work and providing valuable input. Dr. Arjan Kuijper and Dr. Reiner Wichert have accompanied my work over the last years and have been a steady source of constructive criticism, review and new ideas. I would like to thank my colleagues and frequent co-authors of the competence center for Interactive Multimedia Appliances at the Fraunhofer Institute for Computer Graphics Research IGD for discussing and sharing ideas that shaped this work. A special thanks to Pascal Hamisu, who introduced me to the magical world of capacitive sensors. My thanks also go to the different Bachelor and Master students I had the opportunity to supervise over the last years - in chronological order Arthur Fischer, Tobias Große-Puppendahl, Martin Majewski, Yannick Berghöfer, Stephan Neumann, Stefan Krepp, Sebastian Frank and Sebastian Zander-Walz. Likewise, without the competent aid of numerous student workers this work would not have been possible. So my thanks additionally goes to Henning Heggen, Sönke Schmidt, Mark Prediger, Steeven Zeiß, Maxim Djakow and Pia Weiß. Finally, I would like to express my thanks to my family and friends for patience, encouragement and support during the last years.
