\begin{appendix}
\input{eval_results.tex}

\chapter{Publications}
The thesis is partially based on the following publications:

\begin{description}
\item[2013]{\bf OpenCapSense: A Rapid Prototyping Toolkit for Pervasive Interaction Using Capacitive Sensing} (Tobias Grosse-Puppendahl, Yannick Berghoefer, Andreas Braun, Raphael Wimmer, Arjan Kuijper), {\em In IEEE International Conference on Pervasive Computing and Communications (PerCom)}, volume 18, pp. 22, 2013.
\item[2012]{\bf V2me: Evaluating the first steps in mobile friendship coaching} (Salla Muuraiskangas, Anja K Leist, Andreas Braun, Kerstin Klauß, Peter H M P Roelofsma, Reiner Wichert, Peter Klein, Dieter Ferring), {\em In Journal of Ambient Intelligence and Smart Environments}, IOS Press, volume 4, pp. 517-534, 2012.
\item[2011]{\bf User requirements in ICT-based social media use: Acceptance of a virtual coach} (Anja Leist, Dieter Ferring, Kerstin Klauss, Peter Klein, Andreas Braun, Reiner Wichert), {\em In }, 2011.
\item[2014]{\bf V2me - Virtual Coaching for Seniors} (Andreas Braun, Silvana Cieslik, René Zmugg, Reiner Wichert, Peter Klein, Sven Havemann), {\em In Wohnen – Pflege – Teilhabe - Besser leben durch Technik. 7. Deutscher AAL-Kongress}, VDE Verlag, 2014.
\item[2013]{\bf User requirements for navigation assistance in public transit for elderly people} (Stefanie Müller, Felix Kamieth, Andreas Braun, Tim Dutz, Peter Klein), {\em In Proceedings of the 6th International Conference on PErvasive Technologies Related to Assistive Environments}, pp. 55, 2013.
\item[2013] {\bf Swiss-cheese extended: an object recognition method for ubiquitous interfaces based on capacitive proximity sensing} (Tobias Grosse-Puppendahl, Andreas Braun, Felix Kamieth, Arjan Kuijper), {\em In Proceedings of the 2013 ACM annual conference on Human factors in computing systems}, pp. 1401-1410, 2013.
\item[2013]{\bf Context-based bounding volume morphing in pointing gesture applications} (Andreas Braun, Arthur Fischer, Alexander Marinc, Carsten Stocklöw, Martin Majewski), {\em In HCII'13 Proceedings of the 15th international conference on Human-computer interaction}, Springer Berlin Heidelberg, pp. 147-156, 2013.
\item[2013]{\bf Capacitive sensor-based hand gesture recognition in ambient intelligence scenarios} (Andreas Braun, Tim Dutz, Felix Kamieth), {\em In Proceedings of the 6th International Conference on PErvasive Technologies Related to Assistive Environments}, pp. 5, 2013.
\item[2013]{\bf Marker-Free Indoor Localization and Tracking of Multiple Users in Smart Environments Using a Camera-Based Approach} (Andreas Braun, Tim Dutz, Michael Alekseew, Philipp Schillinger, Alexander Marinc), {\em In Distributed, Ambient and Pervasive Interactions}, 2013.
\item[2012]{\bf Honeyfish - a high resolution gesture recognition system based on capacitive proximity sensing} (Tobias Grosse-Puppendahl, Andreas Braun), {\em In Embedded World Conference 2012}, Haar: WEKA Fachmedien, 2012 (Design \& Elektronik), pp. 10pp, 2012.
\item[2012]{\bf Context recognition using capacitive sensor arrays in beds} (Andreas Braun, Henning Heggen), {\em In Technik für ein selbstbestimmtes Leben - 5. Deutscher AAL-Kongress}, VDE VERLAG GmbH, 2012.
\item[2012]{\bf Visual Support System for Selecting Reactive Elements in Intelligent Environments} (Martin Majewski, Andreas Braun, Alexander Marinc, Arjan Kuijper), {\em In International Conference on Cyberworlds}, pp. 251-255, 2012.
\item[2012] {\bf CapFloor – A Flexible Capacitive Indoor Localization System} (Andreas Braun, Henning Heggen, Reiner Wichert), {\em In Evaluating AAL Systems Through Competitive Benchmarking. Indoor Localization and Tracking (Stefano Chessa, Stefan Knauth, eds.)}, Communications in Computer and Information Science, pp. 26-35, 2012.
\item[2011] {\bf Empowering and integrating senior citizens with virtual coaching} (Andreas Braun, Peter H. M. P. Roelofsma, Dieter Ferring, Milla Immonen), {\em In Ambient Intelligence (David V. Keyson, Mary Lou Maher, Norbert Streitz, Adrian Cheok, Juan Carlos Augusto, Reiner Wichert, Gwenn Englebienne, Hamid Aghajan, Ben J. A. Kröse, eds.)}, Springer Berlin Heidelberg, volume 7040, pp. 369-370, 2011.
\item[2011] {\bf Interactive personalization of ambient assisted living environments} (Alexander Marinc, Carsten Stocklöw, Andreas Braun, Carsten Limberger, Cristian Hofmann, Arjan Kuijper), {\em In Proceeding HI'11 Proceedings of the 2011 international conference on Human interface and the management of information}, volume Part I, pp. 567-576, 2011.
\item[2011] {\bf Passive identification and control of arbitrary devices in smart environments} (Andreas Braun, Felix Kamieth), {\em In HCII'11 Proceedings of the 14th international conference on Human-computer interaction: towards mobile and intelligent interaction environments (Julie A. Jacko, ed.)}, Springer-Verlag, pp. 147-154, 2011.
\item[2011] {\bf Adaptive implicit interaction for healthy nutrition and food intake supervision} (Felix Kamieth, Andreas Braun, Christian Schlehuber), {\em In HCII'11 Proceedings of the 14th international conference on Human-computer interaction: towards mobile and intelligent interaction environments}, Springer-Verlag, pp. 205-212, 2011.
\item[2011]{\bf Classification of User Postures with Capacitive Proximity Sensors in AAL-Environments} (Tobias Grosse-Puppendahl, Alexander Marinc, Andreas Braun), {\em In Ambient Intelligence (David V Keyson, Mary Lou Maher, Norbert Streitz, Adrian Cheok, Juan Carlos Augusto, Reiner Wichert, Gwenn Englebienne, Hamid Aghajan, Ben J A Kröse, eds.)}, Springer, volume 7040, pp. 314-323, 2011.
\item[2011] {\bf Designing a multi-purpose capacitive proximity sensing input device} (Andreas Braun, Pascal Hamisu), {\em In Proceedings of the 4th International Conference on PErvasive Technologies Related to Assistive Environments PETRA 11}, ACM Press, 2011.
\item[2010]{\bf Analyse des Schlafverhaltens durch kapazitive Sensorarrays zur Ermittlung der Wirbelsäulenbelastung} (Pascal Hamisu, Andreas Braun), {\em In 3. Deutscher AAL Kongress}, VDE VERLAG GmbH, pp. 3-6, 2010.
\item[2009] {\bf Using the human body field as a medium for natural interaction} (Andreas Braun, Pascal Hamisu), {\em In Proceedings of the 2nd International Conference on PErvsive Technologies Related to Assistive Environments - PETRA '09}, ACM Press, pp. 1-7, 2009.
\item[2012] {\bf Synergieeffekte aus der Kombination verschiedener AAL Lösungen} (Kerstin Klauß, Stefanie Müller, Andreas Braun, Tim Dutz, Felix Kamieth, Peter Klein), {\em In Mensch \& Computer 2012--Workshopband: interaktiv informiert--allgegenwärtig und allumfassend!? (H. Reiterer, O. Deussen, eds.)}, Oldenbourg Verlag, pp. 61-67, 2012.
\item[2013]{\bf Building Up Virtual Environments Using Gestures} (Alexander Marinc, Carsten Stocklöw, Andreas Braun), {\em In Chapter in Universal Access in Human-Computer Interaction. Applications and Services for Quality of Life}, Springer Berlin Heidelberg, pp. 70-78, 2013.
\item[2013]{\bf Providing Visual Support for Selecting Reactive Elements in Intelligent Environments} (Martin Majewski, Andreas Braun, Alexander Marinc, Arjan Kuijper), {\em In Chapter in Transactions on Computational Science XVIII}, Springer, pp. 248-263, 2013.
\item[2013]{\bf Unobtrusive Recognition of Working Situations} (Tobias Grosse-Puppendahl, Sebastian Benchea, Felix Kamieth, Andreas Braun, Christian Schuster), {\em In Chapter in Distributed, Ambient, and Pervasive Interactions}, Springer Berlin Heidelberg, pp. 115-121, 2013.
\item[2013]{\bf AmbiTrack-Marker-free Indoor Localization and Tracking of Multiple Users in Smart Environments with a Camera-based Approach} (Andreas Braun, Tim Dutz), {\em In Chapter in Evaluating AAL Systems Through Competitive Benchmarking}, Springer Berlin Heidelberg, pp. 83-93, 2013.
\item[2012]{\bf Dynamic User Representation in Video Phone Applications} (Andreas Braun, Reiner Wichert), {\em In Chapter in Constructing Ambient Intelligence}, Springer Berlin Heidelberg, pp. 184-188, 2012.
\end{description}

\newpage


\chapter{Supervising Activities}

The following list summarizes the student bachelor, diploma and master thesis supervised by the author. The results of these works were partially used as an input into the thesis.

\section{Diploma and Master Thesis}

\begin{enumerate}
\item Große-Puppendahl, Tobias - Multi-hand Interaction Using Custom Capacitive Proximity Sensors - MSc TU Darmstadt 2012 
\item Berghöfer, Yannick - Human-Machine-Interfaces in Automotive Environments using Capacitive Proximity Sensors - MSc TU Darmstadt 2013
\item Krepp, Stefan - Unobtrusive Surface Touch Recognition using Acoustic Tracking - MSc TU Darmstadt 2014
\end{enumerate}

\section{Bachelor Thesis}

\begin{enumerate}
\item Fischer, Arthur - Unterstützung von zielbasierter Interaktion durch gestenerkennende Zeigegeräte - BSc TU Darmstadt 2012
\item Majewski, Martin - Visual-aided Selection of Reactive Elements in Intelligent Environments - BSc TU Darmstadt 2012
\item Neumann, Stephan - Automotive interfaces using an interactive armrest - BSc TU Darmstadt 2014
\end{enumerate}

\input{cvDiss.tex} 

\end{appendix}




