\chapter{Related Work}
\label{ch:related_work}
In this chapter I will introduce the most relevant literature that inspired this work, or that is required to introduce a specific topic. The aim of this chapter is to provide a basis for both, the benchmarking model that is developed in Chapter \ref{ch:benchmark}, and the capacitive proximity sensing methods described in Chapter \ref{ch:usecases}. The related works are distinguished into four parts. At first, I will give a general introduction to electric field sensing, including a discussion on different properties, physical background, the influence of materials and geometry, as well as different data processing methods. Following that, I will  present relevant applications using capacitive proximity sensing, ranging from historical works to recent systems. In the next section, various sensing technologies are introduced that are used in typical smart environment applications. Finally, I will identify and group different applications in smart environments, providing a basis for the applications covered by the benchmarking model.
\input{chapters/related/electric.tex}
%\clearpage 
\input{chapters/related/capapps.tex}
%\clearpage
\input{chapters/related/sensor_tech.tex}
%\clearpage
\input{chapters/related/applications.tex}

\section{Disucssion}
In this chapter I have given an introduction to electric field sensing, including different properties, physical background and the influence of materials. I have shown a number of applications built upon this technology, ranging from historic examples to research done in the last years. The field of smart environments is diverse and extensive. Thus, in order to identify the aspects relevant for this work I have introduced several multi-purpose sensor technologies that are frequently used in applications for smart environments. Additionally, I have given an overview of application domains within smart environments that are considered candidates for systems based on capacitive proximity sensors. These related works are necessary to motivate the underlying considerations of the benchmarking model that will be presented in the next chapter. It is necessary to have an extensive overview of potential applications and sensor technologies to derive a benchmarking model that successfully links sensor capabilities to features required for certain applications. 