\section{Processing methods}
\label{ch:prot_proc}
After analyzing the challenges associated to the different use cases for capacitive proximity sensor I will use the following section to specify a number of novel or improved data processing methods that can be used in this context. They are grouped into five specific areas:

Sparsely distributed sensor arrays refer to configurations that have a limited number of sensors spread over larger areas. In this regard it is important to find methods that allow acquiring sufficient information about the object to be detected. Typically information about the electrode geometry and interpolation methods are used to meet these requirements.

The second area are model-driven fitting methods. Using a simplified model of the object to be detected, it is possible to fit these to the received sensor data. The area can be distinguished according to the complexity of the models that are either comprised of a single body or multiple parts that are connected to each other.

Heterogeneous sensor systems can be described as a combination of multiple sensors that are not uniform. In terms of capacitive proximity sensors this can refer to either arrays of different capacitive sensors that use a geometric layout of varying sizes and shapes or the combination of capacitive sensors with other categories of sensing systems in a meaningful fashion.

Image-based processing describes the method of creating an image from capacitive sensor data and applying different algorithms associated to visual computing. An uniform array of capacitive proximity sensors resembles an array of light sensors on a different frequency interval of electromagnetic radiation. Thus, with a few limitations it can be treated similar to a camera system with operations applied on a pixel level.

A last group is the processing of physiological signals in time domain and frequency domain. Many physiological activities rely on the movement of muscles, e.g. the beat of the heart or the chest movement associated to breathing. These movements have an effect on the electric field generated by capacitive proximity sensors and can be analyzed using a variety of different methods.

\input{chapters/prototypes/proc_sparse.tex}
\input{chapters/prototypes/proc_model.tex}
\input{chapters/prototypes/proc_hetero.tex}
\input{chapters/prototypes/proc_image.tex}
\input{chapters/prototypes/proc_physio.tex}

