\chapter{Use cases for capacitive proximity sensors}
\label{ch:usecases}
After having defined the potential application domains for capacitive proximity sensors, in the following section I will evaluate the actual use cases by presenting associated challenges, presenting data processing methods on how to tackle them, and present a number of prototypes that have been created by implementing these methods. This allows to gather the information required to discuss the application of capacitive proximity sensors in smart environments and validate their use in Chapter \ref{ch:eval}. In addition to the application specific challenges, there are also numerous challenges in the implementation phase that are detailed in the descriptions of the associated prototypes.

\input{chapters/prototypes/challenges.tex}

\input{chapters/prototypes/processing.tex}
\clearpage

\section{Application prototypes}
In the last few years I have designed a number of different prototypes using capacitive proximity sensors in various usage scenarios within smart environments that were realized with the help of numerous students and colleagues. They tackle specific application domains and implement one or more of the data processing methods that have been specified in the previous section. A short overview can be found in Table \ref{tab:prot_listown}. During the next few pages I will describe in detail how the prototypes have been created, how they implement the different data processing methods and outline the results of any technical evaluation and usability study that has been performed.

% Table generated by Excel2LaTeX from sheet 'Tabelle2'
\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Overview of developed capacitive proximity sensing prototypes}
    \begin{tabularx}{\linewidth}{Xp{3.5cm}Xp{3.5cm}p{3.5cm}}
    \toprule
    \textbf{Name} & \textbf{Description} & \textbf{Application Areas} & \textbf{Measuring Layout} & \textbf{Data Processing} \\
    \midrule
    CapFloor & Capacitive system for indoor localization and fall detection based on electrode grid below the floor. & Indoor Localization & Loading mode, variable number of sensors based on area size & Binary activity association and using geometry for positioning. Monitoring of overall value for falls. \\
    Smart Bed & Capacitive sensors placed below mattress able to determine sleeping postures and breathing rate. & Smart Appliances, Physiological Sensing & Loading mode, four sensors on each side of bed  & Posture fitting using a static model. Fourier analysis for breathing rate recognition. \\
    The Capacitive Chair & Office chair equipped with capacitive sensors to distinguish different typical work postures and stress levels. & Smart Appliances, Physiological Sensing & Loading mode and shunt mode, eight sensors, heterogeneous sensing capabilities & Model fitting using a dynamic model. Fourier analysis for breathing rate detection. Posture recognition using machine learning. \\
    Active Armrest & Heterogeneous system for finger gesture recognition and arm rest identification for automotive applications. & Smart Appliances, Gestural Interaction & Loading mode, heterogeneous layout & Finger positioning using direct calculation. Binary arm presence detection. \\
    MagicBox & Mobile 3D gesture interaction device using an array of electrodes. & Gestural Interaction & Loading mode, six wireless sensor nodes & Geometric detection of hand relative to plane. Adapted mouse methods for gesture recognition. \\
    CapTap & Table capable of detecting 3D gestures and knocks to realize tactile interaction in a living room. & Smart Appliances, Gestural Interaction & Loading mode, 24 capacitive sensors and a single touch detecting microphone & Image-based hand and arm detection. Independent touch detection. Tracking of multiple objects. \\
    \bottomrule
    \end{tabularx}%
  \label{tab:prot_listown}%
\end{table}%

\input{chapters/prototypes/capfloor.tex}
\clearpage
\input{chapters/prototypes/smartbed.tex}
\clearpage
\input{chapters/prototypes/capchair.tex}
\clearpage
\input{chapters/prototypes/armrest.tex}
\clearpage
\input{chapters/prototypes/magicbox.tex}
\clearpage
\input{chapters/prototypes/captap.tex}
\clearpage
\input{chapters/prototypes/other_proto.tex}
\clearpage
\input{chapters/prototypes/related_proto.tex}

\section{Discussion}
In this chapter I have identified several distinct use cases for capacitive proximity sensors in smart environments and their associated challenges. Based on this, new and improved processing methods in five different areas have been proposed. These are sparsely distributed sensor system, model-based approaches, heterogeneous sensor systems, image-based processing and physiological sensing. The methods have been implemented and evaluated using a set of six prototypes, that are suited for one or more application areas. This has been put into context with some additional collaborative prototypes and systems known from literature. The rationale of designing the sensor layout and the different processing methods are detailed in the specific sections. Overall, this allows to get a knowledge base that enables me to evaluate the applicability of capacitive proximity sensors in smart environments. The next chapter will describe this evaluation, that is based on a comparison to the other introduced sensor technologies and the specific benefits and limitations of capacitive proximity sensors. The primary purpose is to develop a set of guidelines for parties interested in developing applications for smart environments that are based on capacitive proximity sensors.