\section{Benefits}
\begin{table}[htbp]
  \centering
  \caption{Overview of capacitive proximity sensing benefits}
    \begin{tabular}{p{4cm}p{6cm}}
    \toprule
    \textbf{Name} & \textbf{Examples} \\
    \midrule
    \textbf{Versatility} & Flexible electrode design, scalability, different sensing methods \\
    \textbf{Unobtrusiveness} & Invisible application, non-disturbing frequency range \\
    \textbf{Processing Complexity} & Small number of sensors, variable dynamic range \\
    \bottomrule
    \end{tabular}%
  \label{tab:cap_benefits}%
\end{table}%

Given the information collected in the previous section we can now talk about the specific benefits of capacitive proximity sensing. We are using three different groups for categorization, namely versatility, unobtrusiveness and processing complexity. Some examples within these groups are shown in Table \ref{tab:cap_benefits}. In the following section I will discuss those groups in detail.
\subsection{Versatility}
A main benefit of capacitive proximity sensors is the versatility in which they can be applied. With flexible choice of electrode materials, size and geometry it is possible to create highly individual applications. Example electrodes include transparent metal oxide layers, woven conductive thread, copper wires, PCB boards or simple aluminum foil. 

Additionally, the sensor systems are also highly scalable. By choosing appropriate voltages and frequencies it is possible to add a high number of sensors to a single object. Using smart measurement windows and different multiplexing methods, sensors can be placed close together and electrodes may act as both sender and receiver.
The different sensing methods presented - loading mode, shunt mode and transmit mode enable a variety of different sensing patterns. The human body can be used as both sender and receiver and smart electrode layouts allow using low-powered processors. 

In conclusion, it is possible to add capacitive sensing to most everyday objects to enable different forms of interaction, create natural interfaces and smart objects. Our prototypes are using different electrode materials, flexible or solid electrodes, conductive thread, wires, shielded or non-shielded layouts.
 
\subsection{Unobtrusiveness}
Electric fields are not usually perceived by persons, unless they are of exceptional strength. Furthermore, they propagate through many materials that are typically present in our environment, including most plastics, wood or tile. This allows us to invisibly apply capacitive proximity sensors without a strong effect on the measurement. Application below several centimeters of covering is possible, if the electrodes are designed properly for large distance sensing.

The frequency range in which the sensors are operating is usually not in an interval that disturbs other electronic systems. Thus it is feasible to use capacitive sensing even in environments, where non-disturbance is a main requirement.  Additionally the used frequencies are not considered to be biologically active, and good results can be achieved using small currents. 

It is possible to equip most conductive objects directly with capacitive proximity sensors and hide them below non-conductive objects with minimal spatial requirements. Our Smart Bed and Active Armrest prototypes are using sensor sets that are completely invisible from the outside and communicate wireless to a PC only using a power supply. .
 
\subsection{Processing Complexity}
An appropriate analogy to capacitive proximity sensors is a single photo diode. As opposed to a light intensity we are measuring capacitance. While the information we can gain from such a measurement is limited, the processing required to analyze the signal is also low. Performing signal analysis on an array of 24 capacitive sensors, as in the CapTap prototype (Section \ref{ch:prot_captap}) is comparable to processing the image of a 6x4 pixel camera. Therefore, it is easy to create highly integrated systems with low-power devices for performing any subsequent data analysis. 

While it is possible and in many cases beneficial to use complex data processing algorithms for object detection, it is in many cases possible to achieve a similar result with less complex methods. In many applications it is even viable to opt for a quantized capacitance measurement. In the case of a touch sensor a single binary measure is sufficient. However, it is also possible to select various different levels and reduce the dynamic range to an easily computable value that is 4 or 8 Bit long. Depending on the chosen algorithm this dynamic range reduction can occur either in pre-processing or high-level processing. 

With the exception of the Capacitive Chair (Section \ref{ch:prot_capchair}) and the CapTap that make extensive use of frequency domain operations, our prototypes are using simple data processing methods that can be easily applied on embedded systems. One of the presented examples is the weighted average algorithm for object detection. Regarding model-based data processing, even very simple cylindrical models, such as the one used for the Smart Bed (Section \ref{ch:prot_smartbed}), are capable to reliably predict numerous postures that are relevant in real world applications. In general, the low requirements for data pre-processing, allows dedicating more resources to high-level data processing algorithms if the specific application is resource constrained. 

The OpenCapSense toolkit that is the base for most of our prototypes has a fairly powerful micro controller that is able to implement all of the processing steps - thus enabling highly integrated, low-power capacitive proximity sensing prototypes that can be used in smart environment applications.
