\chapter{Evaluating capacitive proximity sensors in smart environments}
\label{ch:eval}
In the previous chapters I have presented background information on capacitive proximity sensors and decribed various prototypes of this technology, in different application domains within smart environments. These overviews included both an analysis of existing prototypes from literature, as well as a collection of own prototypes that were developed in the last years. With this as a basis, it is now possible to perform a meta-analysis to identify common patterns and identify benefits and limitations of the technology within smart environments. This chapter is distinguished into four different parts. First, I will compare capacitive proximity sensing to other sensing technologies that are commonly used in smart environments. The limitations and benefits of the technology are identified and discussed in detail. I will conclude with a set of guidelines that may help other researchers when designing smart environment applications based on capacitive proximity sensors. This discussion is extended from a current working paper \cite{braun2014capjaise}.
\input{chapters/evaluation/eval_tech.tex}
%\clearpage
\input{chapters/evaluation/benefits.tex}
%\clearpage
\input{chapters/evaluation/limitations.tex}
%\clearpage
\input{chapters/evaluation/guidelines.tex}

\section{Discussion}
In this chapter I have evaluated capacitive proximity sensors in smart environments. The first step of this evaluation was to establish a comparison to other sensor technologies. Those are commonly used in smart environment applications and have been introduced in the related works. This comparison allowed me to determine specific benefits and limitations of capacitive proximity sensors, in relation to both other sensing technologies and the specific requirements of applications in smart environments. This builds the foundation to create a set of guidelines that support parties developing smart environment applications throughout the development process, from choosing a sensor technology, over designing the hardware, to selecting suitable algorithms for processing the data.